{\boldmath Pseudoscalar top-Higgs coupling: Exploration of $\mathrm{CP}$-odd observables to resolve the sign ambiguity }

### 2016-03-03 Paper_ttbarH_Draft.tex
KK edit -- part way through Sec. IV

\section{{\boldmath $\mathrm{CP}$}-odd observables not depending on \MakeLowercase{{\boldmath $t$}} and \MakeLowercase{{\boldmath $\tbar$}} spin vectors}
\label{sec4}
So far we have considered three TPs involving the momenta $t,\tbar$
and $Q$ and the spin vectors $n_t$ and $n_{\tbar}$ given in
Eqs.~(\ref{eq3})-(\ref{eq4}). In fact, we have described the general
form of the differential cross-section in terms of these vectors in
Eq.~(\ref{eq20}). Here, we will take into account another
possibilities for the choice of the vectors from which the
$\mathrm{CP}$-odd observables can be constructed. From the definitions
in Eqs.~(\ref{eq3})-(\ref{eq4}), we see that the TPs
$\epsilon_{1,2,3}$ can be written as follows,
\label{eq29}
\TPa = \frac{m^2_t}{(t\cdot \ell^+)(\tbar\cdot \ell^-)}\,\epsilon(t,\tbar,\ell^-\!,\ell^+),
\vspace*{1mm}
\label{eq30}
\TPb = \frac{m^2_t}{(t\cdot \ell^+)(\tbar\cdot \ell^-)}\left(\epsilon(t,\tbar,\ell^-\!,\ell^+)+\epsilon(H,\tbar,\ell^-\!,\ell^+)+\frac{(t\cdot\ell^+)}{m^2_t}\epsilon(H,\tbar,t,\ell^-\!)\right)
\vspace*{1mm}
\label{eq31}
\TPc = \frac{m^2_t}{(t\cdot \ell^+)(\tbar\cdot \ell^-)}\left(-\epsilon(t,\tbar,\ell^-\!,\ell^+)+\epsilon(H,t,\ell^-\!,\ell^+)+\frac{(\tbar\cdot\ell^-)}{m^2_t}\epsilon(H,\tbar,t,\ell^+\!)\right).
\vspace*{2mm}
The above equations express the TPs studied in the last sections as
linear combination of TPs involving the momenta $t,\tbar,H,\ell^+$ and
$\ell^-$, with coefficients that are functions of phase space
variables. These five momenta give rise to five TPs whose sensitivity
can also be tested by means of the observables introduced in
Secs.~\ref{sec3.1}-\ref{sec3.3}. In the first place, we have found
that TPs not including both lepton and anti-lepton momenta present a
negligible sensitivity, and then we will concentrate here on the
results obtained for the remaining TPs,
$\epsilon_5\equiv\epsilon(t,\tbar,\ell^-\!,\ell^+),
\epsilon_6\equiv\epsilon(H,t,\ell^-\!,\ell^+)$ and $\epsilon_7\equiv
\epsilon(H,\tbar,\ell^-\!,\ell^+)$. The Tables \ref{table6} and
\ref{table7} summarize the results for these TPs.
\renewcommand{\arraystretch}{1.6}
\caption{Mean values obtained for the TPs $\epsilon_{5,6,7}$ for the
  SM case and two $\mathrm{CP}$-mixed cases with opposite sign in the
  pseudoscalar coupling. The values correspond to $10^5$ simulated
  events.}
\label{table6}
\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}||C{2cm}||C{2cm}|}
%\hhline{|=====|}
\hhline{|-----|}
$\kappa_t$ & $\tilde{\kappa}_t$ & $\langle \epsilon_5 \rangle /\sigma_{\bar{\epsilon}_5}$ & $\langle \epsilon_6 \rangle /\sigma_{\bar{\epsilon}_6}$ & $\langle \epsilon_7 \rangle /\sigma_{\bar{\epsilon}_7}$ \\ 
\hhline{|=====|} 
%\hhline{|-----|}
%\vspace*{.5mm}
\renewcommand{\arraystretch}{1.0}
$1$~ & $-1$~~~ & $3.98$~ & $-1.96$~~~ & $1.69$~ \\[0.6mm]
$1$ & $0$~ & $-0.43$~~~ & $1.25$~ & $0.74$~ \\[0.6mm]
$1$ & $1$~ & $-6.76$~~~ & $3.46$~ & $-3.29$~~~~\\[0.6mm]
\hhline{|=====|}
%\hhline{|-----|}
\renewcommand{\arraystretch}{1.4}
\caption{Asymmetries for the TPs $\epsilon_{5,6,7}$ for the SM case
  and the two $\mathrm{CP}$-mixed cases defined by $\kp=1,\kpt=\pm
  1$. The values correspond to $10^5$ simulated events.}
\label{table7}
$\kappa_t$&$\tilde{\kappa}_t$~~&$\mathcal{A}(\epsilon_5)$~~&$\mathcal{A}(\epsilon_5)/\sigma_{\mathcal{A}}$& $\mathcal{A}(\epsilon_6)$~~&$\mathcal{A}(\epsilon_6)/\sigma_{\mathcal{A}}$&$\mathcal{A}(\epsilon_7)$~~&$\mathcal{A}(\epsilon_7)/\sigma_{\mathcal{A}}$  \\ 
$1$ & $-1$~~~ & $0.0315$~ & $10.0$~ & $-0.0134$~~~ & $-4.2$~~~ & $0.0111$~ & $3.5$~\\[0.6mm]
$1$ & $0$ & $-0.0021$~~~ & $-0.7$~~~ & $-0.0011$~~~ & $-0.3$~~~ & $0.0009$~& $0.3$~\\[0.6mm]
$1$ & $1$ & $-0.0379$~~~ & $-12.0$~~~ & $0.0143$~ & $4.5$~ & $-0.0137$~~~ & $\,-4.3$~~~  \\[0.6mm]

@@

for which the asymmetries and mean values are comparable (see Tables

@@

$\epsilon_5$ is exactly the same as for $\epsilon_1$ as was expected

@@

Tables \ref{table5} and \ref{table6} that the TPs $\epsilon_{1,2,3}$

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section{{\boldmath $\mathrm{CP}$}-odd observables not depending on \MakeLowercase{{\boldmath $t$}} and \MakeLowercase{{\boldmath $\tbar$}} spin vectors}
\label{sec4}
So far we have considered three TPs involving the momenta $t,\tbar$
and $Q$ and the spin vectors $n_t$ and $n_{\tbar}$ [defined in
Eqs.~(\ref{eq3})-(\ref{eq4}].  Furthermore, we have described the general
form of the differential cross-section in terms of these vectors in
Eq.~(\ref{eq20}). In this section we consider other
possibilities for the choice of the vectors from which the
$\mathrm{CP}$-odd observables can be constructed. From the definitions
in Eqs.~(\ref{eq3})-(\ref{eq4}), we see that the TPs
$\epsilon_{1,2,3}$ can be written as follows,
%
\beq
\label{eq29}
\TPa = \frac{m^2_t}{(t\cdot \ell^+)(\tbar\cdot \ell^-)}\,\epsilon(t,\tbar,\ell^-\!,\ell^+),
\eeq
%
\vspace*{1mm}
\beq
\label{eq30}
\TPb = \frac{m^2_t}{(t\cdot \ell^+)(\tbar\cdot \ell^-)}\left(\epsilon(t,\tbar,\ell^-\!,\ell^+)+\epsilon(H,\tbar,\ell^-\!,\ell^+)+\frac{(t\cdot\ell^+)}{m^2_t}\epsilon(H,\tbar,t,\ell^-\!)\right) \,,
\eeq
%
\vspace*{1mm}
\beq
\label{eq31}
\TPc = \frac{m^2_t}{(t\cdot \ell^+)(\tbar\cdot \ell^-)}\left(-\epsilon(t,\tbar,\ell^-\!,\ell^+)+\epsilon(H,t,\ell^-\!,\ell^+)+\frac{(\tbar\cdot\ell^-)}{m^2_t}\epsilon(H,\tbar,t,\ell^+\!)\right).
\vspace*{2mm}
\eeq
%
The above equations express the TPs studied in the last sections as
linear combination of TPs involving the momenta $t,\tbar,H,\ell^+$ and
$\ell^-$, with coefficients that are functions of phase space
variables. These five momenta give rise to five TPs whose sensitivity
can also be tested by means of the observables introduced in
Secs.~\ref{sec3.1}-\ref{sec3.3}.  Now, we have found
that TPs not including both the lepton and anti-lepton momenta yield
negligible sensitivity to the value of $\kpt$.  For this reason,
we concentrate here on the
results obtained for the remaining TPs,
%
\beq
\label{eqa5}
\epsilon_5\equiv\epsilon(t,\tbar,\ell^-\!,\ell^+) \,,
\vspace*{1mm}
\eeq
%
\beq
\label{eqa6}
\epsilon_6\equiv\epsilon(H,t,\ell^-\!,\ell^+) \,,
\vspace*{1mm}
\eeq
%
\beq
\label{eqa7}
\epsilon_7\equiv\epsilon(H,\tbar,\ell^-\!,\ell^+) \,.
\vspace*{1mm}
\eeq
%
    {\bf (KK: Should we clarify somehow that $\epsilon_{4,5,6,7}$ are not the same as
      $\epsilon_{4,5,6,7}$ in Eq.~(20)?  That seems like a potential source of confusion.)}

\renewcommand{\arraystretch}{1.6}
\begin{table}[H]
\caption{Mean values obtained for the TPs $\epsilon_{5,6,7}$ for the
  SM case and two $\mathrm{CP}$-mixed cases with opposite sign in the
  pseudoscalar coupling. The values correspond to $10^5$ simulated
  events.}
\label{table6}
\begin{center}
\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}||C{2cm}||C{2cm}|}
%\hhline{|=====|}
\hhline{|-----|}
$\kappa_t$ & $\tilde{\kappa}_t$ & $\langle \epsilon_5 \rangle /\sigma_{\bar{\epsilon}_5}$ & $\langle \epsilon_6 \rangle /\sigma_{\bar{\epsilon}_6}$ & $\langle \epsilon_7 \rangle /\sigma_{\bar{\epsilon}_7}$ \\ 
\hhline{|=====|} 
%\hhline{|-----|}
%\vspace*{.5mm}
\renewcommand{\arraystretch}{1.0}
$1$~ & $-1$~~~ & $3.98$~ & $-1.96$~~~ & $1.69$~ \\[0.6mm]
\hline
$1$ & $0$~ & $-0.43$~~~ & $1.25$~ & $0.74$~ \\[0.6mm]
\hline
$1$ & $1$~ & $-6.76$~~~ & $3.46$~ & $-3.29$~~~~\\[0.6mm]
\hhline{|=====|}
%\hhline{|-----|}
\end{tabular}
\end{center} 
\end{table}
\renewcommand{\arraystretch}{1.4}
\begin{table}[H]
\caption{Asymmetries for the TPs $\epsilon_{5,6,7}$ for the SM case
  and the two $\mathrm{CP}$-mixed cases defined by $\kp=1,\kpt=\pm
  1$. The values correspond to $10^5$ simulated events.}
\label{table7}
\begin{center}
\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}|}
%\begin{tabular}{|c|r||r|c||r|c||r|c|}
\hhline{|========|}
%\hhline{|--------|}
$\kappa_t$&$\tilde{\kappa}_t$~~&$\mathcal{A}(\epsilon_5)$~~&$\mathcal{A}(\epsilon_5)/\sigma_{\mathcal{A}}$& $\mathcal{A}(\epsilon_6)$~~&$\mathcal{A}(\epsilon_6)/\sigma_{\mathcal{A}}$&$\mathcal{A}(\epsilon_7)$~~&$\mathcal{A}(\epsilon_7)/\sigma_{\mathcal{A}}$  \\ 
\hhline{|========|} 
%\hhline{|--------|}
$1$ & $-1$~~~ & $0.0315$~ & $10.0$~ & $-0.0134$~~~ & $-4.2$~~~ & $0.0111$~ & $3.5$~\\[0.6mm]
\hline
$1$ & $0$ & $-0.0021$~~~ & $-0.7$~~~ & $-0.0011$~~~ & $-0.3$~~~ & $0.0009$~& $0.3$~\\[0.6mm]
\hline
$1$ & $1$ & $-0.0379$~~~ & $-12.0$~~~ & $0.0143$~ & $4.5$~ & $-0.0137$~~~ & $\,-4.3$~~~  \\[0.6mm]
\hhline{|========|}
%\hhline{|--------|}
\end{tabular}
\end{center} 
\end{table}
\par
%

Tables~\ref{table6} and
\ref{table7} summarize the results for the TPs $\epsilon_{5,6,7}$.
    {\bf (KK: Should we interchange the two tables?  In the previous section
      we considered asymmetries first, then mean values.  Seems like it might
      flow better to follow that same order here.)}

@@

for which the asymmetries and mean values are comparable for the TPs
(see Tables

@@

$\epsilon_5$ is exactly the same as for $\epsilon_1$, as was expected

@@

Tables~\ref{table5} and \ref{table6} that the TPs $\epsilon_{1,2,3}$
